Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-25 papers/ms.tex
update ms

Our goals in fitting the Kepler light curves are twofold.  First, we
want to derive accurate planetary sizes and orbital properties.
Second, we want to remove the stellar variability signal to enable a
statistical assessment of the probability that the transit signals are
planetary.

We fitted the data as follows.  Given the transit
ephemeris from \citet{thompson_planetary_2018}, we first trimmed the
light curve to a local window around each transit that spanned three
transit durations before and after each mid-transit time.  The
out-of-transit points in each local window were then fitted with a
fourth-order polynomial, which was divided out from the light curve.
The resulting flattened transits were then fitted with a transit model
that assumed quadratic limb darkening.  The model therefore included 8
free parameters for the transit ($\{P, t_0, \log R_{\rm p}/R_\star, b,
u_1 ,u_2, R_\star, \log g\}$), 2 free parameters for the light curve
normalization and a white noise jitter ($\{\langle f \rangle, \sigma_f
\}$), and 5 fixed parameters for each transit.

We fitted the models using \texttt{exoplanet}
\citep{exoplanet:exoplanet}.  We assumed a Gaussian likelihood, and
sampled using \texttt{PyMC3}'s No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014}, after having initialized to the the
maximum {\it a posteriori} (MAP) model.  We used the
\citet{gelman_inference_1992} statistic ($\hat{R}$) as our convergence
diagnostic.  The resulting fits are shown in the lower panels of
Figure~\ref{fig:planets}, and the important derived parameters are in
Table~\ref{tab:sysparams}.  The set of full parameters with their
priors are given in Appendix~\ref{app:transit}.

A potential drawback of our approach is that to remove
the starspot-induced variability, we fixed 5 
parameters per transit to their MAP values.
An alternative could be to fit the
planetary transits simultaneously with the starspot-induced
variability using a quasiperiodic Gaussian process (GP).  We explored
this approach, but found that it sometimes required fine-tuning of the
hyperparameter priors, otherwise the GP would overfit flares,
instrumental noise, and any other variability that was not part of the
transit.  This failure mode is pernicious, in that it yields an
ill-founded sense of confidence in a visually clean fit.  Our model is
simpler, and it has the benefit that the white noise jitter never
trades off with any parameter equivalent to a damping timescale for
the coherence of the GP.  It is also computationally efficient, and it
captures the planetary parameters about which we care the most.

@@

In the future, it may be possible to obtain independent evidence for
the planetary nature of the Cep-Her planets, for instance through
transit observations using a high-resolution spectrograph.  For now,
it is of interest whether the transit signals might be astrophysical
false positives, or whether they are statistically more likely to be
planetary.  We adopt the Bayesian framework implemented in
\texttt{VESPA} to assess the relevant probabilities
\citep{morton_efficient_2012,vespa_2015}.  Briefly summarized, the
priors in \texttt{VESPA} assume the binary star occurrence rate from
\citet{raghavan_survey_2010}, direction-specific star counts from
\citet{girardi_star_2005}, and planet occurrence rates as described by
\citet[][Section~3.4]{morton_efficient_2012}.  The likelihoods are
then evaluated by forward-modeling a synthetic population of eclipsing
bodies for each astrophysical model class, in which each population
member has a known trapezoidal eclipse depth, total duration, and
ingress duration.  These summary statistics are then compared against
the actual photometric data to evaluate the probabilities of false
positive scenarios such as foreground eclipsing binaries, hierarchical
eclipsing binaries, and background eclipsing binaries.

\paragraph{Kepler-1643}
Kepler-1643~b (KOI-6186.01) was already validated as a transiting
planet by \citet{morton_false_2016}, who found a probability for any
of the aforementioned false positive scenarios of 9$\times$10$^{-6}$.
Repeating the calculation with our own stellar-variability correction
and the new NIRC2 imaging constraints, we find ${\rm FPP} =
6\times10^{-9}$.  Figure~\ref{fig:planets} shows the justification:
the transit is flat and has a high S/N ($\approx 47$).  The shape is
therefore nearly impossible to reproduce with eclipsing binary models.

Intriguingly, Kepler-1643 failed one of the data validation
centroid shift tests (see the \texttt{q1\_q17\_dr25\_koi} data
release): the angular distance between the target star's catalog
position and the position of the transiting source was measured as
$1\farcs0$ at 4.4-$\sigma$.  The reports show however that two
outlying quarters (2 and 6) drive the offset -- the centroid locations
from the other Kepler quarters are consistent at $\lesssim 0\farcs4$.
Nonetheless, this is an instructive exercise in how stellar
variability complicates centroid-based vetting tests.  The centroid
shifts measured by these tests are determined from the in- and
out-of-transit flux-weighted centroids.  For stars with significant
spot-induced variability there is no static baseline in either the in-
or out-of-transit phases.

\paragraph{KOI-7368}
KOI-7368.01 is listed on the NASA Exoplanet Archive as a ``candidate''
planet.  \citet{morton_false_2016} did not compute a false positive
probability for the system because their default trapezoidal fitting
routine failed, presumably due to the spot-induced variability.  Our
fitting approach rectifies this point, and our new NIRC2 images
revealed no new stellar companions.  Performing the relevant
calculation, we find ${\rm FPP} \approx 4\times10^{-3}$.  Though not
as convincing as Kepler-1643, this clears the usual threshold
for calling the planet statistically validated
\citep{morton_efficient_2012}.  The S/N of the transit is
$\approx$$32$, which indicates that it is unlikely to be caused by
systematic noise in the light curve (see Figure~\ref{fig:planets}).
The positional probability score also meets the requirements for
transiting sources thought to share positions with their target stars
\citep{2017ksci.rept...16B}.

It bears mentioning that KOI-7368 shows a weak centroid shift in the
\texttt{q1\_q17\_dr25\_koi} validation reports, similar to
Kepler-1643.  For KOI-7368, the reported offset is smaller, and less
statistically significant ($0\farcs2$; 3.0-$\sigma$).  Again, the data
validation reports show that the shift is caused by a few outlying
quarters (4, 5, 8, and 12).  The fact that the remaining data show a
consistent scatter between centroid locations suggests that these
outliers are also caused by the stellar variability.  Independently,
our NIRC2 imaging shows that there are no neighboring sources that
could cause an offset of the observed amplitude.

\paragraph{KOI-7913}
KOI-7913.01 is also currently listed on the NASA Exoplanet Archive as a
``candidate'' planet.  The canonical \citet{morton_false_2016}
analysis was of Q1-Q17 KOIs from DR24, and therefore spanned KOI-1.01
to KOI-7620.01 and omitted KOI-7913.01.  However the results of the
subsequent DR25 analysis by Morton et al.\ are listed at the NASA
Exoplanet Archive.  The relevant table gives a probability for the
system being an astrophysical false positive of $1.4\times10^{-4}$,
with the most likely false positive scenario being a blended eclipsing
binary.  Repeating the calculation with our new detrending and
contrast curves, we find a similar result: ${\rm FPP} =
1.3\times10^{-4}$.  Though the transit has the lowest S/N of any of
the objects discusssed (${\rm S/N}=14$), its lower FPP relative to
KOI-7368 can be understood through its flat-bottomed shape,
combined with its long transit duration relative to plausible
eclipsing binary models (Figure~\ref{fig:planets}).  The host star
probability usability score \citep{2017ksci.rept...16B} also meets the
usual threshold, and so the planet seems to be validated.  Its
disposition has however previously fluctuated from ``false positive''
to ``candidate''.  The most likely explanation is the presence of
KOI-7913~B, which is located approximately one Kepler pixel away from
Kepler-7913 A (see Appendix~\ref{app:koi7913}).  Our pixel-level
analysis of the target pixel files did not show any evidence to
support the idea that KOI-7913~B could host the transiting planet.
Our NIRC2 imaging similarly ruled out the possibility of any other
plausible host star for the planet other than KOI-7913~A.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ages more precise than a
    factor of three are emphasized. The Cep-Her planets are
    Kepler-1643~b ($\square$), KOI-7368~b ($\triangledown$),
    KOI-7913~Ab (X), and Kepler-1627~Ab (+).  Interesting trends in
    the population of young planets include {\it i)} their
    large sizes and {\it ii)} the lack of young hot Jupiters.  The new
    objects of interest in Cep-Her have normal mini-Neptune sizes
    between 2 and 3\,$R_\oplus$, which is a novelty given their ages.
    Parameters are from the NASA Exoplanet Archive (2022 Apr 5).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

The most significant novelty about Kepler-1643~b, KOI-7368.01, and
KOI-7913~Ab is that their sizes are normal, relative to the known
population of gigayear-old mini-Neptunes.  At field star ages,
mini-Neptune sizes span 1.8\,$R_\oplus$ to 3.6\,$R_\oplus$, with the
most common size being $\approx 2.4\,R_\oplus$
\citep[][Figure~7]{Fulton_et_al_2017}.  The known planets younger than
$10^8$ years are almost all larger, with sizes between 4 and
10$\,R_\oplus$
\citep{Mann_K2_33b_2016,David_et_al_2016,benatti_possibly_2019,david_four_2019,newton_tess_2019,rizzuto_tess_2020,bouma_cluster_2020,mann_toi1227_2022}.
Figure~\ref{fig:rp_period_age} explores this in more detail by showing
the sizes, orbital periods, and ages of the known transiting planets,
emphasizing planets with precise ages.  The smallest previously known
planets comparable to the new Cep-Her mini-Neptunes are AU~Mic~c
($3.0\pm0.2\,R_\oplus$, see \citealt{martioli_aumicbc_2021} and
\citealt{gilbert_flares_2022}), Kepler-1627~Ab ($3.8\pm0.2\,R_\oplus$;
\citealt{bouma_kep1627_2022}), and AU~Mic~d ($4.2\pm0.2\,R_\oplus$;
\citealt{plavchan_planet_2020}).

The theoretical expectation is that mini-Neptunes with sizes of 2 to
3\,$R_\oplus$ should be common at ages of $10^7$ to $10^8$ years.
This expectation is tied to inferences about the initial distributions
of planetary core mass, core composition, and atmospheric mass
fraction \citep{owen_evaporation_2017}.  The Kelvin-Helmholtz cooling
timescale, which is tied to the entropy of the planetary interior once
the disk disperses, could also play a significant role
\citep{owen_constraining_2020}.  As an example,
\citet{rogers_unveiling_2021} predicted that given a core-mass
distribution peaked at $\approx$$4$\,$M_\oplus$, an ice-poor rock/iron
core composition, and a typical H/He mass fraction of $\approx$4\%,
there should be a maximum in planet occurrence at 2 to 3\,$R_\oplus$
at times between 10 and 100\,Myr.  The models
advanced by \citet{gupta_signatures_2020} and
\citet{lee_primordial_2021} agree; their differences lie in the mechanism
for producing the radius valley.  If the radius valley is
primordial and created by gas accretion physics, then super-Earths
($<$$1.8$\,$R_\oplus$) would be common as early as $10^7$ years
\citep{lee_primordial_2021}.   The photoevaporation-driven models more
often quote $10^8$ year timescales for production of
atmosphere-stripped super-Earths, while the models with the mass-loss
driven by a slow escape of heat from the core predict longer
$\sim$$10^9$ year timescales (but see \citealt{king_2021}).

Systems such as K2-25, V1298~Tau, HIP-67522, TOI-837, and TOI-1227
have sizes that are much larger than the picture we have just
described.  However, their large sizes can be accommodated by existing
models by invoking any of {\it i)} larger core masses, {\it ii)} more
volatile-rich compositions, {\it iii)}  larger initial atmospheric
mass fractions, or {\it iv)} longer thermal cooling times.  For
instance, perhaps all five of the the aforementioned systems are large
because the planets are more massive than most mini-Neptunes.
Secure mass measurements would help constrain this parameter space,
but the $\sim$1\,\kms\ spot-induced radial velocity semi-amplitudes
makes measuring the Doppler orbits very difficult.
\citep[][]{cale_diving_2021,zicher_one_2022,klein_one_2022}.
Regardless, the new Kepler-1643, KOI-7368, and KOI-7913 systems do
demonstrate that at least some planets at 40\,Myr have sizes that are
consistent with theoretical expectations for mini-Neptunes.  While
selection effects imposed by spot-induced photometric variability are
a likely explanation for why planets this small have not previously
been identified \citep[{e.g.},][]{zhou_2021_tois}, future work should
quantify this bias more carefully, in order to enable empirical
studies of how the planetary size distribution changes at early times.

@@

\paragraph{Cep-Her}
Our analysis to date has focused only on portions of Cep-Her that were
observed by Kepler: RSG-5, CH-2, and the $\delta$~Lyr cluster.  In
\citet{bouma_kep1627_2022} as well as this work, we have shown that
these groups share similar ages, and have kinematic correlations that
suggest a common origin.  With that said, the membership and
kinematics of the other subgroups shown in Figure~\ref{fig:XYZvtang}
deserve independent attention.  An important aspect of the work that
remains will be to acquire radial velocities of a large subset of the
stars, to assess whether the traceback approach could be applicable.
Wide-field spectroscopic surveys such as LAMOST
\citep{zhao_2012_LAMOST} or SDSS-V \citep{kollmeier_2017} could enable
such analyses, while also providing sensitivity to the Li 6708\,\AA\
line.  Gaia DR3 may also provide RVS spectra for the brighter F and G
dwarfs; these would contain the calcium infrared triplet as another
age indicator.  These indicators, combined with better kinematics,
will be needed to definitively unravel the formation history of the
complex.

A number of worthy photometric projects also seem possible given the
new understanding of Cep-Her.  One is asteroseismology of the
$\delta$~Sct stars, using either TESS or Kepler data
\citep{bedding_very_2020}.  For cases in which the modes are resolved,
this might yield age or metallicity estimates for the subgroups
independent of other approaches.  Other projects could include
searches of the Kepler light curves for exocomets
\citep{zieba_transiting_2019}, and for missed planets around the most
rapid rotators.

\paragraph{Exoplanet demographics at early times}
Our main motivation for finding new young planets is to help benchmark
models for planetary evolution.  However demographic analyses of the
known planets between $10^7$ and $10^9$ years have so far been
somewhat limited.  Approximately 40 such planets are now known
(Figure~\ref{fig:age}).  About half come from K2, a quarter from TESS,
and now a quarter from Kepler.

Given the current state of the field, a few reflections regarding
experimental design of a demographic survey focused on planetary
evolution over the first gigayear might be useful.  The first is
that such a project requires a set of target stars with known ages.
A promising way to compile relevant stars could be to
combine automated spatio-kinematic clustering from Gaia with
rotation periods measured using TESS \citep[see the appendices
of][]{bouma_kep1627_2022}.  The second consideration is that the known
young planets smaller than $3$\,$R_\oplus$ all come from either K2 or
Kepler.  Demographic inferences based on TESS are therefore limited to
planetary sizes $\gtrsim4$\,$R_\oplus$, for planets close-in to their
host stars.  It seems worthwhile to compare the absolute occurrence
rate of such planets to those observed by Kepler.  One specific
question that seems within reach would be to clarify whether enough
young stars have been searched for the dearth of young hot Jupiters to
be significant.  Since the hot Jupiter occurrence rate is strongly
dependent on stellar mass and metallicity
\citep{petigura_metallicity_2018,petigura_cksX_2022}, particular care
would be needed to select a sample of well-studied FGK dwarfs for the
measurement, likely using stars in Sco OB2, Cep-Her, and Orion.  For
demographic studies focused on how mini-Neptune sizes evolve, the
combined K2 and Kepler dataset might be the better primary source.

@@

We have shown that Kepler-1643~b, KOI-7368~b, and KOI-7913~Ab are 40
to 50 million years old, and that each system is most likely
planetary.  The evidence for the planetary interpretation comes from
an application of \texttt{VESPA} to the Kepler data, alongside new
imaging from NIRC2.  The validity of the \texttt{VESPA} framework
rests on the premise that non-astrophysical false positives can be
rejected.  Kepler-1643 and KOI-7368 both pass all but one of the
canonical vetting tests: the check for centroid offsets between the in
and out-of-transit phases.  For both cases, the weak observed shifts
seem to be caused by starspot-induced variability in specific quarters
spuriously moving the stellar center-of-light.  Independently, our
imaging rules out companion stars at the brightness and positions that
would be needed to explain the reported shifts.

Each system has multiple indicators of youth that support the reported
ages.  For Kepler-1643, the strongest youth indicator is its physical
and kinematic association with RSG-5.  Based on the color-absolute
magnitude diagram, we are able to select members of this cluster with
a false positive rate of a few percent (Figure~\ref{fig:age}).
Kepler-1643 is one such member.  While the stellar rotation period
period agrees with this assessment, the star's lithium equivalent
width is somewhat low, which might motivate future exploration of
lithium depletion across FGKM stars in RSG-5 (see
Appendix~\ref{app:spectra}).

@@

The astrophysical significance of these considerations is that planets
$\sim$2 Earth radii in size exist at ages of 40 million years.  It
will be interesting to continue the push down to smaller planetary
sizes at comparable ages -- the planetary detections we have presented
are well above the average detection significance for Kepler planets.
There may still be room at the bottom.

@@

\clearpage
\bibliographystyle{yahapj}                            
\bibliography{bibliography}

>>>>

Our goals in fitting the Kepler light curves are twofold.  First, we
want to derive accurate planetary sizes and orbital properties.
Second, we want to remove the spot-induced variability signal to enable a
statistical assessment of the probability that the transit signals are
planetary.

We fitted the data as follows.  Given the transit
ephemeris from \citet{thompson_planetary_2018}, we first trimmed the
light curve to a local window around each transit that spanned three
transit durations before and after each transit midpoint.  The
out-of-transit points in each local window were then fitted with a
fourth-order polynomial, which was divided out from the light curve.
The resulting flattened transits were then fitted with a transit model
that assumed quadratic limb darkening.  The model therefore included 8
free parameters for the transit ($\{P, t_0, \log R_{\rm p}/R_\star, b,
u_1 ,u_2, R_\star, \log g\}$), 2 free parameters for the light curve
normalization and a white noise jitter ($\{\langle f \rangle, \sigma_f
\}$), and 5 fixed parameters for each transit.

We fitted the data using \texttt{exoplanet}
\citep{exoplanet:exoplanet}.  We assumed a Gaussian likelihood, and
sampled using \texttt{PyMC3}'s No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014}, after having initialized to the the
maximum {\it a posteriori} (MAP) model.  We used the
\citet{gelman_inference_1992} statistic, $\hat{R}$, as our convergence
diagnostic.  The resulting fits are shown in the lower panels of
Figure~\ref{fig:planets}, and the important derived parameters are in
Table~\ref{tab:sysparams}.  The set of full parameters and their
priors are given in Appendix~\ref{app:transit}.

A potential drawback of our approach is that to remove
the starspot-induced variability, we fixed 5 
parameters per transit to their MAP values.
An alternative could be to fit the
planetary transits simultaneously with the starspot-induced
variability using a quasiperiodic Gaussian process (GP).  We explored
this approach, but found that it often required fine-tuning of the
hyperparameter priors, otherwise the GP would overfit flares,
instrumental noise, and any other variability that was not part of the
transit.  This failure mode is pernicious, in that it yields an
ill-founded sense of confidence in a visually clean fit.  Our model is
simpler, and it has the benefit that the white noise jitter never
trades off with any parameter equivalent to a damping timescale for
the coherence of the GP.  It is also computationally efficient, and it
captures the planetary parameters about which we care the most.

@@

In the future, it may be possible to obtain independent evidence for
the planetary nature of the Cep-Her planets, for instance by observing
spectroscopic transits.  For now,
it is of interest whether the transit signals might be astrophysical
false positives, or whether they are statistically more likely to be
planetary.  We adopt the Bayesian framework implemented in
\texttt{VESPA} to assess the relevant probabilities
\citep{morton_efficient_2012,vespa_2015}.  Briefly summarized, the
priors in \texttt{VESPA} assume the binary star occurrence rate from
\citet{raghavan_survey_2010}, direction-specific star counts from
\citet{girardi_star_2005}, and planet occurrence rates as described by
\citet[][Section~3.4]{morton_efficient_2012}.  The likelihoods are
then evaluated by forward-modeling a synthetic population of eclipsing
bodies for each astrophysical model class, in which each population
member has a known trapezoidal eclipse depth, total duration, and
ingress duration.  These summary statistics are then compared against
the actual photometric data to evaluate the probabilities of false
positive scenarios such as foreground eclipsing binaries, hierarchical
eclipsing binaries, and background eclipsing binaries.

\paragraph{Kepler-1643}
Kepler-1643~b (KOI-6186.01) was already validated as a transiting
planet by \citet{morton_false_2016}, who found a probability for any
of the aforementioned false positive scenarios of 9$\times$10$^{-6}$.
Repeating the calculation with our own stellar-variability correction
and the new NIRC2 imaging constraints, we find ${\rm FPP} =
6\times10^{-9}$.  Figure~\ref{fig:planets} shows the justification:
the transit is flat and has a high S/N ($\approx$$47$).  The shape is
therefore nearly impossible to reproduce with eclipsing binary models.

Intriguingly, Kepler-1643 failed one of the data validation
centroid shift tests (see the \texttt{q1\_q17\_dr25\_koi} data
release): the angular distance between the target star's catalog
position and the position of the transiting source was measured as
$1\farcs0$ at 4.4-$\sigma$.  The reports show however that two
outlying quarters (2 and 6) drive the offset -- the centroid locations
from the other Kepler quarters are consistent at $\lesssim 0\farcs4$.
This is an instructive exercise in how stellar
variability complicates centroid-based vetting tests.  The 
shifts measured by these tests are determined from the in- and
out-of-transit flux-weighted centroids.  For stars with significant
spot-induced variability there is no static baseline in either the in-
or out-of-transit phases.

\paragraph{KOI-7368}
KOI-7368.01 is listed on the NASA Exoplanet Archive as a ``candidate''
planet.  \citet{morton_false_2016} did not compute a false positive
probability for the system because their default trapezoidal fitting
routine failed, presumably due to the spot-induced variability.  Our
fitting approach rectifies this point, and our new NIRC2 images
revealed no new stellar companions.  Performing the relevant
calculation, we find ${\rm FPP} = 4\times10^{-3}$.  Though not
as convincing as Kepler-1643, this clears the usual threshold
for calling the planet statistically validated
\citep{morton_efficient_2012}.  The S/N of the transit is
$\approx$$32$, which indicates that it is unlikely to be caused by
systematic noise in the light curve (see Figure~\ref{fig:planets}).
The positional probability score also meets the requirements for
transiting sources thought to share positions with their target stars
\citep{2017ksci.rept...16B}.

It bears mentioning that KOI-7368 shows a weak centroid shift in the
\texttt{q1\_q17\_dr25\_koi} validation reports, similar to
Kepler-1643.  For KOI-7368, the reported offset is smaller, and less
significant ($0\farcs2$; 3.0-$\sigma$).  Again, the data
validation reports show that the shift is caused by a few outlying
quarters (4, 5, 8, and 12).  The fact that the remaining data show a
consistent scatter between centroid locations suggests that these
outliers are also caused by the stellar variability.  
Our NIRC2 imaging independently shows that there are no neighboring
sources that could cause an offset of the observed amplitude.

\paragraph{KOI-7913}
KOI-7913.01 is also currently listed on the NASA Exoplanet Archive as a
``candidate'' planet.  The \citet{morton_false_2016}
analysis was of Q1-Q17 KOIs from DR24, and therefore spanned KOI-1.01
to KOI-7620.01 (omitting KOI-7913.01).  However the results of the
subsequent DR25 analysis by Morton et al.\ are listed at the NASA
Exoplanet Archive.  The relevant table gives a probability for the
system being an astrophysical false positive of $1.4\times10^{-4}$,
with the most likely false positive scenario being a blended eclipsing
binary.  Repeating the calculation with our new detrending and
contrast curves, we find a similar result: ${\rm FPP} =
1.3\times10^{-4}$.  Though the transit has the lowest S/N of any of
the objects discusssed ($\approx$$14$), its lower FPP relative to
KOI-7368 can be understood through its flat-bottomed shape,
combined with its long transit duration relative to plausible
eclipsing binary models (Figure~\ref{fig:planets}).  The host star
probability usability score \citep{2017ksci.rept...16B} also meets the
usual threshold, and so the planet is statistically validated.  Its
disposition has however previously fluctuated from ``false positive''
to ``candidate'' (see Appendix~\ref{app:koi7913}).  The most likely
explanation is the presence of KOI-7913~B, which is located
approximately one Kepler pixel away from Kepler-7913 A.  Our
pixel-level analysis of the target pixel files did not show any
evidence to support the idea that KOI-7913~B could host the transiting
planet.  Our NIRC2 imaging similarly ruled out the possibility of any
other plausible host star for the planet other than KOI-7913~A.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ages more precise than a
    factor of three are emphasized. The Cep-Her planets are
    Kepler-1643~b ($\square$), KOI-7368~b ($\triangledown$),
    KOI-7913~Ab (X), and Kepler-1627~Ab (+).  Interesting trends in
    the population of $<10^8$ year old planets include {\it i)} their
    large sizes and {\it ii)} the lack of hot Jupiters.  The new
    objects of interest in Cep-Her have normal mini-Neptune sizes
    between 2 and 3\,$R_\oplus$, which is a novelty given their ages.
    Parameters are from the NASA Exoplanet Archive (2022 Apr 5).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

The most significant novelty about the planets in Kepler-1643, KOI-7368, and
KOI-7913 is that their sizes are normal relative to the known
population of mini-Neptunes from Kepler.  At field star ages,
mini-Neptune sizes span 1.8\,$R_\oplus$ to 3.6\,$R_\oplus$, with the
most common size being $\approx 2.4\,R_\oplus$
\citep[][Figure~7]{Fulton_et_al_2017}.  The known planets younger than
$10^8$ years are almost all larger, with sizes between 4 and
10$\,R_\oplus$
\citep{Mann_K2_33b_2016,David_et_al_2016,benatti_possibly_2019,david_four_2019,newton_tess_2019,rizzuto_tess_2020,bouma_cluster_2020,mann_toi1227_2022}.
Figure~\ref{fig:rp_period_age} explores this in more detail by showing
the sizes, orbital periods, and ages of the known transiting planets,
emphasizing planets with precise ages.  The smallest previously known
planets comparable to the new Cep-Her mini-Neptunes are AU~Mic~c
($3.0\pm0.2\,R_\oplus$, see \citealt{martioli_aumicbc_2021} and
\citealt{gilbert_flares_2022}), Kepler-1627~Ab ($3.8\pm0.2\,R_\oplus$;
\citealt{bouma_kep1627_2022}), and AU~Mic~d ($4.2\pm0.2\,R_\oplus$;
\citealt{plavchan_planet_2020}).

The theoretical expectation is that mini-Neptunes with sizes of 2 to
3\,$R_\oplus$ should be common at ages of $10^7$ to $10^8$ years.
This expectation is tied to inferences about the initial distributions
of planetary core mass, core composition, and atmospheric mass
fraction \citep{owen_evaporation_2017}.  The Kelvin-Helmholtz cooling
timescale, which is tied to the entropy of the planetary interior
shortly after
disk dispersal, also plays a significant role
\citep{owen_constraining_2020}.  As an example,
\citet{rogers_unveiling_2021} predicted that given a core-mass
distribution peaked at $\approx$$4$\,$M_\oplus$, an ice-poor rock/iron
core composition, and a typical H/He mass fraction of $\approx$4\%,
there should be a maximum in planet occurrence at 2 to 3\,$R_\oplus$
at times between 10 and 100\,Myr.  The models
advanced by \citet{gupta_signatures_2020} and
\citet{lee_primordial_2021} agree; their differences lie in the mechanism
for producing the radius valley. 
% If the radius valley is
% primordial and created by gas accretion physics, then super-Earths
% ($<$$1.8$\,$R_\oplus$) would be common as early as $10^7$ years
% \citep{lee_primordial_2021}.   The photoevaporation-driven models more
% often quote $10^8$ year timescales for production of
% atmosphere-stripped super-Earths, while the models with the mass-loss
% driven by a slow escape of heat from the core predict longer
% $\sim$$10^9$ year timescales (but see \citealt{king_2021}).

Systems such as K2-25, V1298~Tau, HIP-67522, TOI-837, and TOI-1227
have sizes that are anomalously large relative to the predicted peak
in planet occurrence at 2 to 3\,$R_\oplus$.
However, their large sizes can be accommodated 
by invoking any of {\it i)} larger core masses, {\it ii)} more
volatile-rich compositions, {\it iii)}  larger initial atmospheric
mass fractions, or {\it iv)} longer thermal cooling times.  
Secure mass measurements would help constrain this parameter space,
but the $\sim$1\,\kms\ spot-induced radial velocity semi-amplitudes
makes measuring the Doppler orbits very difficult.
\citep[][]{cale_diving_2021,zicher_one_2022,klein_one_2022}.
Regardless, the new Kepler-1643, KOI-7368, and KOI-7913 systems do
demonstrate that at least some planets at 40\,Myr have sizes that are
consistent with theoretical expectations for mini-Neptunes.  While
selection effects imposed by spot-induced photometric variability are
a likely explanation for why planets this small have not previously
been identified \citep[{e.g.},][]{zhou_2021_tois}, future work should
quantify this bias more carefully, in order to enable empirical
studies of how the planetary size distribution changes at early times.

@@

\paragraph{Cep-Her}
Our analysis to date has focused only on portions of Cep-Her that were
observed by Kepler: RSG-5, CH-2, and the $\delta$~Lyr cluster.  In
\citet{bouma_kep1627_2022} as well as this work, we have shown that
these groups share similar ages, and have kinematic correlations that
suggest a common origin.  With that said, the membership and
kinematics of the other Cep-Her groups shown in Figure~\ref{fig:XYZvtang}
deserve independent attention.  An important aspect of the work that
remains will be to acquire radial velocities of a large subset of the
stars, to assess whether the traceback approach could be applicable.
Wide-field spectroscopic surveys such as LAMOST
\citep{zhao_2012_LAMOST} or SDSS-V \citep{kollmeier_2017} could enable
such analyses, while also providing sensitivity to the Li 6708\,\AA\
line.  If Gaia DR3 provides RVS spectra for the brighter F and G
dwarfs, these would also contain the calcium infrared triplet as another
age indicator.  These indicators, combined with better kinematics,
would help in definitively unravelling the formation history of the
complex.

A number of worthy photometric projects also seem possible given the
new understanding of Cep-Her.  One is asteroseismology of the
$\delta$~Sct stars, using either TESS or Kepler data
\citep{bedding_very_2020}.  For cases in which the modes are resolved,
this might yield age or metallicity estimates for the subgroups
independent of other methods.  Other projects could include
searches of the Kepler light curves for exocomets
\citep{zieba_transiting_2019}, and for missed planets around the most
rapid rotators.

\paragraph{Exoplanet demographics at early times}
Our main motivation for finding new young planets is to help benchmark
models for planetary evolution.  However demographic analyses of the
known planets between $10^7$ and $10^9$ years have so far been
rather limited.  Approximately 40 such planets are now known
(Figure~\ref{fig:age}).  About half come from K2, a quarter from TESS,
and now a quarter from Kepler.

Given the current state of the field, a few reflections regarding
experimental design of a demographic survey focused on planetary
evolution over the first gigayear might be useful.  The first is
that such a project requires a set of target stars with known ages.
A promising way to compile relevant stars could be to
combine automated spatio-kinematic clustering from Gaia with
rotation periods measured using TESS \citep[see the appendices
of][]{bouma_kep1627_2022}.  The second consideration is that all the known
young planets smaller than $3$\,$R_\oplus$ come from either K2 or
Kepler.  Demographic inferences based on TESS are therefore limited to
planetary sizes $\gtrsim4$\,$R_\oplus$, for planets close-in to their
host stars.  It would be worthwhile to compare the occurrence
rates of both types of planets with those from the main Kepler sample.  One specific
question that seems within reach would be to clarify whether enough
young stars have been searched for the dearth of young hot Jupiters to
be significant.  Since the hot Jupiter occurrence rate is strongly
dependent on stellar mass and metallicity
\citep{petigura_metallicity_2018,petigura_cksX_2022}, particular care
would be needed to select a sample of well-studied FGK dwarfs for the
measurement, likely using stars in Sco OB2, Cep-Her, and Orion.  For
demographic studies focused on how mini-Neptune sizes evolve, the
combined K2 and Kepler dataset would be the better primary source.

@@

We have shown that Kepler-1643~b, KOI-7368~b, and KOI-7913~Ab are 40
to 50 million years old, and that each system is most likely
planetary.  The evidence for the planetary interpretation comes from
an application of \texttt{VESPA} to the Kepler data, alongside new
imaging from NIRC2.  The validity of the \texttt{VESPA} framework
rests on the premise that non-astrophysical false positives can be
rejected.  Kepler-1643 and KOI-7368 both pass all but one of the
canonical vetting tests: the check for centroid offsets between the in
and out-of-transit phases.  For both cases, the weak observed shifts
are consistent with being caused by starspot-induced variability in
specific quarters spuriously moving the stellar center-of-light.
Independently, our imaging rules out companion stars with the brightness
and positions that would be needed to otherwise explain the reported shifts.

Each system has multiple indicators of youth that support the reported
ages.  For Kepler-1643, the strongest youth indicator is its physical
and kinematic association with RSG-5.  Based on the color-absolute
magnitude diagram, we are able to select members of this cluster with
a false positive rate of a few percent (Figure~\ref{fig:age}).
Kepler-1643 is one such member.  While the stellar rotation period
period agrees with this assessment, the star's lithium equivalent
width is marginally low, which might motivate future exploration of
lithium depletion across FGKM stars in RSG-5 (see
Appendix~\ref{app:spectra}).

@@

The astrophysical implicatoin of these considerations is that planets
$\approx$2 Earth radii in size exist at ages of 40 million years.  It
will be interesting to continue the push down to smaller planetary
sizes at comparable ages -- the planetary detections we have presented
are well above the average detection significance for Kepler planets.
There may still be room at the bottom.

@@

%\clearpage
\bibliographystyle{yahapj}                            
\bibliography{bibliography}
